\section{Recommendations}
\subsection{Ground-track}
This simulation has not been able to show the ground-track the satellite goes through. As a future improvement this simulation should be able to show the trace that a satellite has on the ground.
\subsection{Earth's rotation}
This simulation has not been able to show the rotation of the earth as the satellite moves around the earth. However, this does not reduce the accuracy of the program in determining the satellites position along it orbit rather it decreases the ability to trace the ground track of the satellite. As a future improvement this simulation should be able to show the earth moving about its axis.

\subsection{Pertubations}
This simulation has not been able to show the effects of perturbations mentioned earlier on the satellite's position along its orbit. This can be done by deriving equations that govern perturbations on the satellite. As a future improvement this simulation should be able to show the effects of perturbations on the satellites motion.

\subsection{Realtime location}
As a future improvement this simulation should be able to locate the subject satellite in realtime. It was not possible for this case because of the recommendations mentioned above. Ideally, one should be able to determine the ground track to successfully for one to locate the satellite correctly.

\subsection{Conclusions}
The objectives of this project were fully met as we were able to simulate the satellite's motion of 1KUNS-PF in 3 dimensions. The accuracy of up to 12 decimal places was satisfactory.

Future improvements can be made to make the program more accurate and include many bodies to the simulation.