\documentclass[12pt,twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{caption}
\usepackage{subcaption}
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{TOWARDS A THREE-BODY PROBLEM}
\fancyfoot{}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[LO,CE]{Chapter \thechapter}
\fancyfoot[CO,RE]{Sylvance Mbaka}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\usepackage[style=authoryear,sorting=none]{biblatex}
\addbibresource{references.bib}

\usepackage{color}
\usepackage{listings}
\usepackage{setspace}
\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{0.98,0.98,0.98}
\lstdefinelanguage{Python}{
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=1em,
	xleftmargin=1em,
	framextopmargin=2em,
	framexbottommargin=2em,
	showspaces=false,
	showtabs=false,
	showstringspaces=false,
	frame=l,
	tabsize=4,
	% Basic
	basicstyle=\ttfamily\small\setstretch{1},
	backgroundcolor=\color{Background},
	% Comments
	commentstyle=\color{Comments}\slshape,
	% Strings
	stringstyle=\color{Strings},
	morecomment=[s][\color{Strings}]{"""}{"""},
	morecomment=[s][\color{Strings}]{'''}{'''},
	% keywords
	morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
	keywordstyle={\color{Keywords}\bfseries},
	% additional keywords
	morekeywords={[2]@invariant,pylab,numpy,np,scipy},
	keywordstyle={[2]\color{Decorators}\slshape},
	emph={self},
	emphstyle={\color{self}\slshape},
	%
}

\title{TOWARDS A THREE-BODY PROBLEM}
\author{Sylvance Mbaka}
\date{26th October 2018}

\begin{document}

\input{titlepage}

\input{abstract}

\chapter*{Declaration}
I  hereby  declare  that  this  research proposal is  my  own work,  and  has  not  been  submitted  at  any  other university  for  purposes  of  examination  or  as  a  research  proposal.  All  sources  used  have  been  acknowledged  by  means  of  proper  references.

\vspace{0.9cm}
\textbf{Sylvance Kerandi Mbaka}\\
\\
Signature: .....................................\\
Date: .............................................\\

This  research  proposal  has  been  submitted  with  the  approval  from  my  supervisor: \\
Dr. Okeyo George Maumba\\
Lecturer, Department of Physics\\
Email: maumba@uonbi.ac.ke\\
University of Nairobi\\
Nairobi, Kenya.\\

\textbf{Dr. Okeyo George Maumba}\\
\\
Signature: .....................................\\
Date: .............................................\\

\chapter*{Dedication}
To my two siblings, mum and dad. To future endeavors.

\chapter*{Acknowledgements}
I want to thank the department of physics for imparting the skills that have led to this project. I would like to thank my supervisor, Dr Maumba, for inspiring me to undertake this line of research. I thank God for everything.

\tableofcontents

\listoffigures

\listoftables

\chapter{Introduction}
\input{chapters/introduction}

\chapter{Literature Review}
\input{chapters/chapter02}

\chapter{Theoretical Input: Two-Body Problem}
\input{chapters/chapter03}

\chapter{Methodology}
\input{chapters/chapter04}

\chapter{Results and Discussion}
\input{chapters/chapter05}

\chapter{Recommendations and Conclusions}
\input{chapters/conclusion}

\begin{thebibliography}{1}
	
	\bibitem{bib1}
	Peter Fortescue, John Stark, Graham Swinerd.
	\newblock {\em \mbox{Spacecrafts Engineering Systems} }, Wiley, 2003.
	
	\bibitem{bib2}
	Aamport.Oliver Montenbruck, Eberhard Gill.
	\newblock {\em \mbox{Satellite Orbits} }, Springer, 2001.
	
	\bibitem{bib3}
	Roger R. Bate, Donald D. Mueller, Jerry E. White.
	\newblock {\em \mbox{Fundamentals of Astrodynamics}  }, Dover, 1971.
	
	\bibitem{bib4}
	Jon Toellner.
	\newblock \(https://www.youtube.com/watch?v=U_KJtzJl5_c \),\\
	\newblock {\em \mbox{Orbital Dynamics The Two Body Problem}}, Youtube, 2018.
	
	\bibitem{bib5}
	Brittanica of Science.
	\newblock \(www.britannica.com/science/celestial-mechanics-physics\),
	\newblock {\em \mbox{Celestial Mechanics Physics}}, Brittanica of Science, 2018.    
	
	
\end{thebibliography}

\appendix
\chapter{Appendix Title}
\input{chapters/appendix}

\end{document}
